\begin{enumerate}[leftmargin=0.45cm, itemsep=0em, topsep=0.5em, parsep=0.2em]
    \item \textbf{Pignatelli, E.}, Toni, L., 2022. \textit{A Survey of Temporal Credit Assignment in Deep Reinforcement Learning}. In submission.
%     \item \textbf{Pignatelli, E.}, Toni, L., 2022. \textit{The Optimal Credit Problem in Reinforcement Learning}. In submission.
    \item Wong N., Meshkinfamfard S., Turbé V., Whitaker M., Moshe M., Bardanzellu A., Dai T., \textbf{Pignatelli E.}, Barclay W., Darzi A., Elliott P., Ward H., Tanaka R., Cooke G., McKendry R., Atchison C., Bharath A., 2022. \textit{Machine learning to support visual auditing of home-based lateral flow immunoassay self-test results for SARS-CoV-2 antibodies}. \textbf{Communications Medicine. Nature Research}.
    \item Lino, M., Cantwell, C., Fotiadis, S., \textbf{Pignatelli, E.}, Bharath, A., 2020. \textit{Simulating Surface Wave Dynamics with Convolutional Networks}. In \textbf{NeurIPS} workshop on Interpretable Inductive Biases and Physically Structured Learning.
    \item Fotiadis, S., \textbf{Pignatelli, E.}, Valencia, M.L., Cantwell, C., Storkey, A., Bharath, A.A., 2020. \textit{Comparing recurrent and convolutional neural networks for predicting wave propagation}. In \textbf{ICLR} Workshop on Deep Neural Models and Differential Equations.
    \item Di Rosario, \textbf{S., Pignatelli}, E. and Mirra, G., 2018, May. \textit{An automated design methodology for acoustic shells in outdoor concerts}. In Proceedings of the \textbf{EuroNoise} (Vol. 2018, pp. 2123-2130).
    \item \textbf{Pignatelli, E.}, Mirra, G. and Pone, S., 2017, September. \textit{InFormer: designing forming actions in post-formed gridshells by means of Multi-Objective Genetic Algorithms}. In Proceedings of \textbf{IASS} Annual Symposia (Vol. 2017, No. 17, pp. 1-10). International Association for Shell and Spatial Structures (IASS).
    \item Mirra, G., \textbf{Pignatelli, E.} and Pone, S., 2016, September. \textit{Computational morphogenesis and construction of an acoustic shell for outdoor chamber music}. In Proceedings of \textbf{IASS} Annual Symposia (Vol. 2016, No. 17, pp. 1-10). International Association for Shell and Spatial Structures (IASS).
    \item Pone, S., Mirra, G., \textbf{Pignatelli, E.}, Lancia, D. and Colabella, S., 2016, October. \textit{Specialised algorithms for different project stages in a post-formed timber gridshell design}. In Proceedings of the 3rd International Conference on Structures and Architecture \textbf{(ICSA)} (pp. 259-266).
    \item Di Rosario, S., Parenti, B., \textbf{Pignatelli, E.}, Mirra, G., Pone, S., 2015, October. \textit{Res, Resonant String Shell, development and design of an acoustic shell for outdoor chamber music concerts}. In Proceedings of the \textbf{Institute of Acoustics} (Vol. 37, pp. 354-373). 9th International Conference on Auditorium Acoustics.
    \item \textbf{Pignatelli, E.}, Colabella, S., Rosario, S.D. and Pone, S., 2015, August. \textit{A wooden acoustic shell for open-air chamber music concert}. In Proceedings of \textbf{IASS} Annual Symposia (Vol. 2015, No. 25, pp. 1-12). International Association for Shell and Spatial Structures (IASS).
\end{enumerate}
