\begin{awards}
    \begin{enumerate}[leftmargin=0.45cm, itemsep=0em, topsep=0.5em, parsep=0.2em]
        \item
        \position{Nomination for ``UCL Inspiring Teaching Delivery Award''}
        \jobdescription{Members of staff who deliver exceptional teaching, using innovative and engaging methods to hold students' interest and help you to learn.}
        \item
        \position{TMLR Survey certification for ``A survey of Temporal Credit Assignment in Deep Reinforcement Learning''}
        \jobdescription{Papers that not only meet the criteria for acceptance but also provide an exceptionally thorough or insightful survey of the topic or approach may be awarded this certification.}
        \item
        \position{UK Research and Innovation Studentship}
        \jobdescription{Including 4 years funding to spend at the University College London for a PhD in Reinforcement Learning.}
        \item
        \position{Best Innovation 2020 – Society of Digital Engineering}
        \jobdescription{For the design of the open-source \textit{Buildings and Habitats Object Model} (bhom.xyz), \textit{to democratise the access to computational engineering}.}
        \item
        \position{Peter Lord Award}
        \jobdescription{Conferred by the Institute of Acoustics to the ReS Team, for the work “\textit{ReS, Resonant String Shell, Development and Design of an Acoustic Shell for Outdoor Chamber Music Concerts” as “a project that showcases outstanding and innovative design}”. 2016.}
        \item
        \position{Honorary Fellowship: Authority in the subject (Cultore della Materia)}
        \jobdescription{In \textit{Technology for Architecture} at the University of Naples Federico II.
        From 2016 to 2018.}
        \item
        \position{Essence of Buro Happold Award}
        \jobdescription{Funding, as part of the Computational Team, Team of the Year, which “\textit{has become an inspiration, the heart of exploring something we do not know where it is going to take us but instinctively is the right thing to do.}” P. Rogers, Senior Partner, 2017.}
        \item
        \position{M.A.R Scholarship – https://www.vpmusica.com/}
        \jobdescription{For the design and construction of the award winning prototype defended in the master’s thesis “\textit{Computational Morphogenesis and Construction of an Acoustic Shell for Outdoor Chamber Music}”. 2015.}
    \end{enumerate}
\end{awards}