\begin{publications}
    \begin{enumerate}[leftmargin=0.45cm, itemsep=0em, topsep=0.5em, parsep=0.2em]
        \item Paglieri D., Cupiał B., Coward S., Piterbarg U., Wolczyk M., Khan A., \emph{Pignatelli E.}, Kuciński Ł., Pinto L., Fergus R., Foerster J. N., Parker-Holder J., Rocktäschel T., 2025. \textit{AgentQuest: Benchmarking LLM and VLM Agents on Long-Horizon Interactive Tasks}. In review at \emph{ICLR} 2025.
        \item \emph{Pignatelli, E.}, Liesen, J., Lange, R.T., Lu, C., Castro, P.S. and Toni, L., 2024.\textit{ NAVIX: Scaling MiniGrid Environments with JAX}. \textbf{RLC} (Reinforcement Learning Conference) 2025. In review.
        \item \emph{Pignatelli, E.}, Ferret, J., Paglieri, D., Coward, S., Tim Rocktäschel, Edward Grefenstette, Toni, L., 2024. \textit{Assessing the Zero-Shot Capabilities of LLMs for Action Evaluation in RL}. \emph{ICML} Workshop on Auto Reinforcement Learning
        \item \emph{Pignatelli, E.}, Ferret, J., Geist, M., Mesnard, T., van Hasselt, H., Toni, L., 2024. \textit{A Survey of Temporal Credit Assignment in Deep Reinforcement Learning}. \emph{TMLR}. \textbf{Awarded Survey Certification.}
        \item A. Kayal, \emph{Pignatelli, E.}, Toni, L., 2023. \textit{Does Behavioural Diversity in Intrinsic Rewards help Exploration?}. In \emph{NeurIPS} Second Agent Learning in Open-Endedness Workshop.
        \item Ntagiantas, K., \emph{Pignatelli, E.}, Peters, N. S., Cantwell, C. D., Chowdhury, R. A., Bharath, A. A., 2023. \textit{Estimation of Fibre Architecture and Scar in Myocardial Tissue Using Electrograms: an in-silico study}. In \textit{Biomedical Signal Processing and Control}.
        \item Wong N., Meshkinfamfard S., Turbé V., Whitaker M., Moshe M., Bardanzellu A., Dai T., \emph{Pignatelli E.}, Barclay W., Darzi A., Elliott P., Ward H., Tanaka R., Cooke G., McKendry R., Atchison C., Bharath A., 2022. \textit{Machine learning to support visual auditing of home-based lateral flow immunoassay self-test results for SARS-CoV-2 antibodies}. \emph{Communications Medicine. Nature Research}.
        \item Lino, M., Cantwell, C., Fotiadis, S., \emph{Pignatelli, E.}, Bharath, A., 2020. \textit{Simulating Surface Wave Dynamics with Convolutional Networks}. In \emph{NeurIPS} workshop on Interpretable Inductive Biases and Physically Structured Learning.
        \item Fotiadis, S., \emph{Pignatelli, E.}, Valencia, M.L., Cantwell, C., Storkey, A., Bharath, A.A., 2020. \textit{Comparing recurrent and convolutional neural networks for predicting wave propagation}. In \emph{ICLR} Workshop on Deep Neural Models and Differential Equations.
        \item Di Rosario, \emph{S., Pignatelli}, E. and Mirra, G., 2018, May. \textit{An automated design methodology for acoustic shells in outdoor concerts}. In Proceedings of the \emph{EuroNoise} (Vol. 2018, pp. 2123-2130).
        \item \emph{Pignatelli, E.}, Mirra, G. and Pone, S., 2017, September. \textit{InFormer: designing forming actions in post-formed gridshells by means of Multi-Objective Genetic Algorithms}. In Proceedings of \emph{IASS} Annual Symposia (Vol. 2017, No. 17, pp. 1-10). International Association for Shell and Spatial Structures (IASS).
        \item \emph{Pignatelli, E.}, Mirra, G., and Pone, S., 2016, September. \textit{Computational morphogenesis and construction of an acoustic shell for outdoor chamber music}. In Proceedings of \emph{IASS} Annual Symposia (Vol. 2016, No. 17, pp. 1-10). International Association for Shell and Spatial Structures (IASS).
        \item Pone, S., Mirra, G., \emph{Pignatelli, E.}, Lancia, D. and Colabella, S., 2016, October. \textit{Specialised algorithms for different project stages in a post-formed timber gridshell design}. In Proceedings of the 3rd International Conference on Structures and Architecture \emph{(ICSA)} (pp. 259-266).
        \item Di Rosario, S., Parenti, B., \emph{Pignatelli, E.}, Mirra, G., Pone, S., 2015, October. \textit{Res, Resonant String Shell, development and design of an acoustic shell for outdoor chamber music concerts}. In Proceedings of the \emph{Institute of Acoustics} (Vol. 37, pp. 354-373). 9th International Conference on Auditorium Acoustics.
        \item \emph{Pignatelli, E.}, Colabella, S., Rosario, S.D. and Pone, S., 2015, August. \textit{A wooden acoustic shell for open-air chamber music concert}. In Proceedings of \emph{IASS} Annual Symposia (Vol. 2015, No. 25, pp. 1-12). International Association for Shell and Spatial Structures (IASS).
    \end{enumerate}
\end{publications}
